A framework for mentored data science research

### 2019-12-08 Rmd/introduction.Rmd
added markdown table

The need to analyze unprecedentedly large volumes of information combined with 
the development of faster and more powerful computers has fueled advances in 
data science methods for big data. Similar causes have led to a
need for greater 
numbers of scientists with quantitative skills. In efforts to enhance training
and mentoring for trainees, we created a program that emphasizes many 
transferable skills that contribute to career success in data science.

We elected to work with social media data. This choice was deliberate. In making 
this decision, we recognized that social media data, such as tweets from 
Twitter, can be acquired with little cost and that there is growing research 
interest in social media in many social science disciplines, including political 
science, communication studies, and sociology. We also anticipated 
that our undergraduate trainees might be intrigued by the possibility of 
analyzing social media data, since many young adults use Facebook, Twitter, 
Instagram, and related sites.

Some social media data, including tweets from Twitter, are 
available through website application product interfaces (APIs). Twitter 
shares, via a streaming API, a sample of approximately one percent of all 
tweets during an API query time period [@tweet_stream].
Researchers have studied tweets for a 
variety of purposes, including 
inference of relationships and social networks among users [@lin2011joint]; 
determination of 
authorship of specific tweets when multiple persons share a single account [@drob]; and 
study of rhetoric in recruiting political supporters [@pelled2018little;@wells2016trump]. 
Recognizing the potential utility of tweets for data science research, we created a 
collection of tweets over time by repeated querying of the Twitter streaming API.

@@

Mentoring in the work place and in higher education can have many 
benefits, including improving students' development as thinkers and scholars, confidence in their 
own abilities, integration into the campus community, and interest in graduate training 
[@baker2010beyond;@higgins2001reconceptualizing].
A key component of our data science mentoring framework is the emphasis on using real data to answer real 
scientific questions. We believe that this process develops problem-solving skills that 
students will need in their future careers in data science. 
We encouraged the student to articulate a scientific research question, translate that question 
into quantitative and statistical terms, determine which data could be used to address the 
question, acquire the data, analyze data, visualize results, and communicate what they learned.

We provide guidance regarding selection of

>>>>

The need to analyze unprecedentedly large volumes of information combined with 
the development of faster and more powerful computers has fueled advances in 
data science methods for big data. Similar causes have led to a
need for greater 
numbers of scientists with quantitative skills. In efforts to enhance training
and mentoring for students, we created a program that emphasizes many 
transferable skills that contribute to career success in data science.

We elected to work with social media data. In making 
this decision, we recognized that social media data, such as tweets from 
Twitter, can be acquired with little cost and that there is growing research 
interest in social media in many social science disciplines, including political 
science, communication studies, and sociology. We also anticipated 
that our undergraduate trainees might be intrigued by the possibility of 
analyzing social media data, since many young adults use Facebook, Twitter, 
Instagram, and related sites.

Some social media data, including tweets from Twitter, are 
available through website application product interfaces (APIs). Twitter 
shares, via a streaming API, a sample of approximately one percent of all 
tweets during an API query time period [@tweet_stream].
Researchers have studied tweets for a 
variety of purposes, including 
inference of relationships and social networks among users [@lin2011joint]; 
determination of 
authorship of specific tweets when multiple persons share a single account [@drob]; and 
study of rhetoric in recruiting political supporters [@pelled2018little;@wells2016trump].
Recognizing the potential utility of tweets for data science research and teaching, 
we created a 
collection of tweets over time by repeated querying of the Twitter streaming API.

@@

Mentoring in the work place and in higher education can have many 
benefits, including improving students' development as thinkers and scholars, confidence in their 
own abilities, integration into the campus community,
and interest in graduate training 
[@baker2010beyond;@higgins2001reconceptualizing].
A key component of our data science mentoring framework is 
the emphasis on using real data to answer 
scientific questions. We believe that this process develops problem-solving skills that 
students will need in their future careers in data science. 
We encouraged students to articulate a scientific research question, translate that question 
into quantitative and statistical terms, determine which data could be used to address the 
question, acquire the data, analyze data, visualize results, and communicate what they learned.
